\textbf{Wavelet Scattering Tranforms Applied to Whale Vocalisations}

### 2024-05-06 dissertation/content/paper2/main.tex
before reference consolodation

\articleinfo{M.W. Rademan, D.J.J Verself, J.A. Du Preez}{Journal of the Acoustical Society of America (JASA)}{15 May 2024}{doi}{Current literature trends for whale classification in passive acoustic monitoring systems are mainly concerned with high accuracies obtained via deep learning approaches. This requires preparation of large and accurate annotated datasets, which are often not available when surveying new regions, nor are they wholly accurate when they are. In contrast to classification, many efforts are still being made in improving generalised detectors for the purpose of disregarding noise. As such, there is a disparity between detectors and classification models.

@@

% \begin{table}[h!]
% \caption{Total number of annotations in the Casey 2017 dataset.}
% \label{tab:numannotations}
% \begin{ruledtabular}  
% \renewcommand{\arraystretch}{0.8}
% \begin{tabular}{lrr} 
% \textbf{Vocalisation}      & \textbf{Number of annotations} & \textbf{Estimated False positives (\%)} \\ \hline
% Bm\_Ant\_A & 1741  & 5 - 10               \\
% Bm\_Ant\_B & 558  & 5 - 10                 \\
% Bm\_Ant\_Z & 119    & 1 - 2               \\
% Bm\_D      & 553     & 8 - 15              \\
% Bp\_20Hz & 78        & 1 - 3             \\
% Bp\_20Plus & 214     & 1 - 3               \\ 
% Total & 3263 & 5 - 10\\ 
% \end{tabular}
% \end{ruledtabular}
% \end{table}

@@

    % \clearpage

    % \section{Summary of parameter values}

    % \begin{table}[h]
        % \caption{Summary of parameter values used in this study. Chosen values are indicated in boldface text, whereas non-bold parameters result from the chosen parameters.}
        % \label{tab:parameters}
        % \begin{ruledtabular}    
            % \renewcommand{\arraystretch}{0.8}% Tighter
            % \begin{tabular}{>{\centering\arraybackslash}l>{\centering\arraybackslash}l>{\centering\arraybackslash}l}  \small
                % \textbf{Parameter}      & \textbf{Description} & \textbf{Value} \\ \hline
                % $T$ & \ac{ws} invariance scale & \textbf{1.5 seconds} \\
                % $Q_1$ & Wavelets per octave in $\mathcal{S}_1$ & \textbf{16} \\
                % $Q_2$ & Wavelets per octave in $\mathcal{S}_2$ & \textbf{4} \\
                % $f_\text{min}$ & Minimum filterbank frequency in $\mathcal{S}_1$ & \textbf{15 Hz}\\
                % $f_\text{max}$ & Maximum filterbank frequency in $\mathcal{S}_1$ & \textbf{120 Hz}\\
                % $|\Lambda_1|$ & Resulting number of filters in $\mathcal{S}_1$ & 48 \\
                % $|\Lambda_2|$ & Resulting number of filters in $\mathcal{S}_2$ & 14 \\
                % $V$ & Wavelet scattering upsample factor & \textbf{2} \\
                % $r$ & Downsampling factor of $\mathcal{U}_1$ due to maximum bandwidth & 8 \\
                % $d$ & Downsampling factor of $\mathcal{S}_1$ & 5 \\
                % $f_{ss}$ & Resulting scattering transform sample frequency & 6.25 Hz \\
                % $B$ & Median filter length for noise coefficient suppression & \textbf{9} \\
                % $D$ & Median filter length for transient coefficient suppression  & \textbf{5 seconds} \\
                % $F$ & Average filter length for noise coefficient estimation  & \textbf{60 seconds} \\
                % $R$ & Median filter length for stabilizing entropy  & \textbf{1.5 seconds} \\
                % $G$ & Maximum filter length for boundary extension  & \textbf{6 seconds} \\
                % $p_t$ & Probability threshold for the whitened \ac{se} \ac{gmm} detector & \textbf{0.3} \\ 
                % $k$ & Dimensions in the classification feature vector $v$ & 521\\ 
                % \end{tabular}
                % \end{ruledtabular}
                % \end{table}

>>>>

\articleinfo{M.W. Rademan, D.J.J Verseld, J.A. Du Preez}{the Journal of the Acoustical Society of America (JASA)}{15 May 2024}{doi}{Current literature trends for whale classification in passive acoustic monitoring systems are mainly concerned with high accuracies obtained via deep learning approaches. This requires preparation of large and accurate annotated datasets, which are often not available when surveying new regions, nor are they wholly accurate when they are. In contrast to classification, many efforts are still being made in improving generalised detectors for the purpose of disregarding noise. As such, there is a disparity between detectors and classification models.

@@

\begin{table}[h!]
\caption{Total number of annotations in the Casey 2017 dataset.}
\label{tab:numannotations}
% \begin{ruledtabular}  
% \renewcommand{\arraystretch}{0.8}
\begin{tabular}{lrr} 
\textbf{Vocalisation}      & \textbf{Number of annotations} & \textbf{Estimated False positives (\%)} \\ \hline
Bm\_Ant\_A & 1741  & 5 - 10               \\
Bm\_Ant\_B & 558  & 5 - 10                 \\
Bm\_Ant\_Z & 119    & 1 - 2               \\
Bm\_D      & 553     & 8 - 15              \\
Bp\_20Hz & 78        & 1 - 3             \\
Bp\_20Plus & 214     & 1 - 3               \\ 
Total & 3263 & 5 - 10\\ 
\end{tabular}
% \end{ruledtabular}
\end{table}

@@

    \section{Summary of parameter values}

    \begin{table}[h]
        \caption{Summary of parameter values used in this study. Chosen values are indicated in boldface text, whereas non-bold parameters result from the chosen parameters.}
        \label{tab:parameters}
        % \begin{ruledtabular}    
            \renewcommand{\arraystretch}{0.8}% Tighter
            \begin{tabular}{lll}  \small
                \textbf{Parameter}      & \textbf{Description} & \textbf{Value} \\ \hline
                $T$ & \ac{ws} invariance scale & \textbf{1.5 seconds} \\
                $Q_1$ & Wavelets per octave in $\mathcal{S}_1$ & \textbf{16} \\
                $Q_2$ & Wavelets per octave in $\mathcal{S}_2$ & \textbf{4} \\
                $f_\text{min}$ & Minimum filterbank frequency in $\mathcal{S}_1$ & \textbf{15 Hz}\\
                $f_\text{max}$ & Maximum filterbank frequency in $\mathcal{S}_1$ & \textbf{120 Hz}\\
                $|\Lambda_1|$ & Resulting number of filters in $\mathcal{S}_1$ & 48 \\
                $|\Lambda_2|$ & Resulting number of filters in $\mathcal{S}_2$ & 14 \\
                $V$ & Wavelet scattering upsample factor & \textbf{2} \\
                $r$ & Downsampling factor of $\mathcal{U}_1$ due to maximum bandwidth & 8 \\
                $d$ & Downsampling factor of $\mathcal{S}_1$ & 5 \\
                $f_{ss}$ & Resulting scattering transform sample frequency & 6.25 Hz \\
                $B$ & Median filter length for noise coefficient suppression & \textbf{9} \\
                $D$ & Median filter length for transient coefficient suppression  & \textbf{5 seconds} \\
                $F$ & Average filter length for noise coefficient estimation  & \textbf{60 seconds} \\
                $R$ & Median filter length for stabilizing entropy  & \textbf{1.5 seconds} \\
                $G$ & Maximum filter length for boundary extension  & \textbf{6 seconds} \\
                $p_t$ & Probability threshold for the whitened \ac{se} \ac{gmm} detector & \textbf{0.3} \\ 
                $k$ & Dimensions in the classification feature vector $v$ & 521\\ 
                \end{tabular}
                % \end{ruledtabular}
                \end{table}
